### 2014-08-25 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add SMV images of exterior

\noindent Table~\ref{tab:incident_timeline} shows an overview of the timeline of events. A plan view of the structure, the location where the downed firefighters were located, and more details of the fire development are provided in the following section.

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 8.53~m (28~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which required approximately 5.1 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh. The domain was divided into 16 meshes (each containing between 289,000 and 346,800 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days. Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes. Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.

% \begin{figure}[!ht]
% \includegraphics[width=6.5in]{../Figures/smv_exterior_grid} \\
% \includegraphics[width=6.5in]{../Figures/smv_exterior_grid_rear}
% \caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
% \label{fig:geom_grid}
% \end{figure}

% \begin{figure}[!ht]
% \includegraphics[width=6.5in]{../Figures/smv_exterior_mesh}
% \caption[Front-right side of the structure within the computational domain.]
% {Front-right side of the structure within the computational domain (with multiple meshes). Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
% \label{fig:mult_mesh}
% \end{figure}

>>>>

\noindent Table~\ref{tab:incident_timeline} shows an overview of the timeline of events. The following section includes a plan view of the structure, the location where the downed firefighters were located, and more details of the fire development.

@@

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 8.53~m (28~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which required approximately 5.1 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh. The domain was divided into 16 meshes (each containing between 289,000 and 346,800 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days. Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes. Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Rear}
\caption{Front (left) and rear (right) of the structure with a 10~cm computational mesh.}
\label{fig:SMV_exterior_grid}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/SMV_Exterior_Meshes}
\caption[Rear-left side of the structure within the computational domain.]
{Rear-left side of the structure within the computational domain (with multiple meshes).}
\label{fig:mult_mesh}
\end{figure}
